CudeleFS: Programmable Consistency and Durability\\in a Global Namespace

### 2017-04-01 paper/sections/5_implementation.tex
paper: wordsmith section 5 and add conclusion/discussion
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

A programmable storage system exposes internal subsystem as building blocks for
higher level services. This `dirty-slate' approach limits redundant code and
leverages the robustness of the underlying storage system. Cudele uses this
approach and re-uses some of the building blocks from the Malacology
programmable storage system~\cite{sevilla:eurosys17} to great success and
requires only:

\begin{itemize}

  \item 354 lines of library code

  \item 219 lines of non-destructive metadata server code, which is not used
  unless it is turned on

  \item 4 lines of destructive client/server code to check whether a namespace
  is decoupled

\end{itemize}

>>>>

We use a ``programmable storage" approach~\cite{sevilla:eurosys17} to design
CudeleFS; namely, we try to leverage components inside Ceph to inherit the
robustness and correctness of the internal subsystems. In this section, we
first describe a Ceph internal subsystem or component and then we show how we
use it in CudeleFS.

### 2017-04-01 paper/sections/6_results.tex
paper: wordsmith section 5 and add conclusion/discussion
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsection{Eventual vs. Strong Consistency}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-weak.png}
\caption{The RPC per metadata update of ``Strong Consistency" has a large
overhead compared to the decoupled namespace strategy of ``Eventual
Consistency".\label{fig:slowdown-strong-weak}}
\end{figure}

@@

\begin{itemize}
  \item Strong Consistency
  \begin{itemize}
    \item[]  \texttt{RPCs} \(+\) \texttt{stream}
  \end{itemize}
  \item Strong Consistency, No Fault Tolerance
  \begin{itemize}
    \item[] \texttt{RPCs}
  \end{itemize}
  \item Eventual Consistency
  \begin{itemize}
    \item[] \texttt{creates} \(+\) \texttt{local persist}
  \end{itemize}
  \item Eventual Consistency, No Fault Tolerance
  \begin{itemize}
    \item[] \texttt{creates} \(+\) \texttt{local persist} \(+\) \texttt{volatile apply}
  \end{itemize}
\end{itemize}

@@

% DeltaFS vs. BatchFS vs. POSIX: decoupled is faster
% (5-7x) vs. (90-104x) slower
% Does not scale?
% Strong Consistency > 10X slower than Eventual Consistency 
\subsubsection{Speedups of Decoupled Namespaces} Eventual consistency uses the
decoupled namespace strategy and shows up to a \(20\times\) speedup over the
traditional namespaces that use RPCs. Compared to the baseline the slowdown is
\(5-7\times\) for Strong Consistency, which emulates BatchFS and
\(90-104\times\) for Eventual Consistency, which emulates DeltaFS.

% POSIX (no stream) vs. POSIX: cost of durability < consistency
\subsubsection{Durability \(<<\) Consistency} The \(1.15\times\) overhead of
``Strong Consistency" compared to ``Strong Consistency, No Fault Tolerance" for
100K files is neglible. It suggests that the overhead of consistency is much
larger than the overhead of durability. This conclusion should be stronger as
we scale the number of files because the cost of streaming the journal into the
object store is constant. We omit the same analysis for ``Eventual Consistency"
because the runtimes are so short that the normalized slowdowns are misleading.

% Eventual Consistency benefit not due to metadata format
\subsubsection{Metadata Formats} Because the metadata formats are the same for
all schemes we argue that the performance gain for decoupled namespaces comes
from relaxing the consistency guarantees and not from the metadata formats, as
was argued in previous work outlining the benefit of
SSTables~\cite{ren:atc2013-tablefs, ren:sc2014-indexfs}.

@@

\subsection{Isolation from EBUSY}

% setup: 2cs sep dirs, 2cs DN, 1c malicious write
In this section, we show the isolation benefits of subtree policies.  We repeat
the experiment from Figure~\ref{fig:interfere-b}, where clients write to their
own private directories and another client interferes at 30 seconds.  We also
have 2 clients write to decoupled namespaces and merge their updates 90
seconds. The

\subsubsection{Benefits of Isolated Subtree Policies}

\subsubsection{Cost of Merging}
\subsubsection{Scaling Concurrent Merges}

\subsection{Isolation from Global Writes, Cost of Overwrites}
\subsection{Cost of Nonvolatile Apply}
% Why so slow?
Creating many files in the same directory would touch the same object but the
existing implementation results in this object being repeatedly pushed/pulled.

@@

>>>>

\subsection{Weak vs. Strong Consistency}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-weak.png}
\caption{The RPC per metadata update of ``Strong Consistency" has a large
overhead compared to the decoupled namespace strategy of ``Weak
Consistency".\label{fig:slowdown-strong-weak}}
\end{figure}

@@

\begin{itemize}
  \item Strong Consistency
  \begin{itemize}
    \item[]  \texttt{RPCs} \(+\) \texttt{stream}
  \end{itemize}
  \item Strong Consistency, No Fault Tolerance
  \begin{itemize}
    \item[] \texttt{RPCs}
  \end{itemize}
  \item Weak Consistency
  \begin{itemize}
    \item[] \texttt{creates} \(+\) \texttt{local persist}
  \end{itemize}
  \item Weak Consistency, No Fault Tolerance
  \begin{itemize}
    \item[] \texttt{creates} \(+\) \texttt{local persist} \(+\) \texttt{volatile apply}
  \end{itemize}
\end{itemize}

@@

% DeltaFS vs. BatchFS vs. POSIX: decoupled is faster
% (5-7x) vs. (90-104x) slower
% Does not scale?
% Strong Consistency > 10X slower than Weak Consistency 
\subsubsection{Speedups of Decoupled Namespaces} Weak consistency uses the
decoupled namespace strategy and shows up to a \(20\times\) speedup over the
traditional namespaces that use RPCs. Compared to the baseline the slowdown is
\(5-7\times\) for Strong Consistency, which emulates BatchFS and
\(90-104\times\) for Weak Consistency, which emulates DeltaFS.

% POSIX (no stream) vs. POSIX: cost of durability < consistency
\subsubsection{Durability \(<<\) Consistency} The \(1.15\times\) overhead of
``Strong Consistency" compared to ``Strong Consistency, No Fault Tolerance" for
100K files is neglible. It suggests that the overhead of consistency is much
larger than the overhead of durability. This conclusion should be stronger as
we scale the number of files because the cost of streaming the journal into the
object store is constant. We omit the same analysis for ``Weak Consistency"
because the runtimes are so short that the normalized slowdowns are misleading.

% Weak Consistency benefit not due to metadata format
\subsubsection{Metadata Formats} Because the metadata formats are the same for
all schemes we argue that the performance gain for decoupled namespaces comes
from relaxing the consistency guarantees and not from the metadata formats, as
was argued in previous work outlining the benefit of
SSTables~\cite{ren:atc2013-tablefs, ren:sc2014-indexfs}.

@@

\subsection{Benefits of Isolated Subtree Policies}
% setup: 2cs sep dirs, 2cs DN, 1c malicious write
In this section, we show the isolation benefits of subtree policies.  We repeat
the experiment from Figure~\ref{fig:interfere-b}, where clients write to their
own private directories and another client interferes at 30 seconds.  We also
have 2 clients write to decoupled namespaces and merge their updates 90
seconds. The

\subsection{Scaling Concurrent Merges}

@@

\subsection{Cost of Nonvolatile Apply}
% Why so slow?
Creating many files in the same directory would touch the same object but the
existing implementation results in this object being repeatedly pushed/pulled.
